---
title: "ETON graphing"
author: "Piotr Chlebicki"
date: '2022-06-05'
output: pdf_document
---

Function that computes $T_{\beta}x=\beta x (mod 1)$

```{r}
Tb <- function(beta) {
  function(x, ign = NULL) {
    (beta * x) %% 1
  }
}
```

Function that computes sum: $$\sum_{x<T_{\beta}^{n}1}\frac{1}{\beta^{n}}$$ 
indecies for which sum will be made are computed as a part of function factory,
condition $T_{\beta}^{n}1\leq (2\cdot\varepsilon)^{\frac{1}{4}}$ is here because 
of computational zeros. Since for large $n$ $\frac{1}{\beta^{n}}\approx 0$ and
we only have finite computational power I'll only check first $2147484$ $n$'s

```{r}
Sigma1b <- function(beta) {
  TbI <- Tb(beta)
  n <- 1
  Vcomp <- NULL
  
  while(n < .Machine$integer.max / 1000) {
    if (Reduce(f = TbI, x = 1:n, init = 1) <= .Machine$double.eps ** .25) {
      n <- n - 1
      break
    }
    n <- n + 1
  }

  Vcomp <- Reduce(f = TbI, x = 1:n, init = 1, accumulate = TRUE)
  
  function(x) {
    if ((x > 1) || (x < 0)) {return(0)}
    TOSUM <- (c(which(x < Vcomp)) - 1)
    sum((1 / beta) ** TOSUM)
  }
}
```

Finally a function that normalises above sum to make it a probability density function:

```{r}
Normalise <- function (f) {
  g <- function(x) {sapply(X = x, FUN = f)}
  
  Constant <- integrate(f = g, 
                        lower = 0, 
                        upper = 1, 
                        rel.tol = .Machine$double.eps ** .5,
                        subdivisions = 100000)$value
  
  function(x) {g(x) / Constant}
}
```

Presentation for $\beta = \varphi = \frac{1+\sqrt{5}}{2}$

```{r}
FF <- Normalise(Sigma1b(beta = (1 + sqrt(5)) / 2))
curve(FF, from = 0, to = 1, n = 10000, 
      ylab = "Probability density function",
      main = expression("Plot of function that defines a measure invariant with respect to " ~ T[beta]),
      xaxt='n')
abline(v = (sqrt(5) - 1) / 2, 
       lty = 2, 
       col = "navy", 
       lwd = 3)
abline(v = 1, 
       lty = 2, 
       col = "navy", 
       lwd = 3)
axis(side = 1, 
     at = c(0, .25, .5, (sqrt(5) - 1) / 2, .75, 1), 
     labels = c(0, .25, .5, expression(1 / beta), .75, 1))
```


A confirmation that FF is a PDF with support on $[0,1]$

```{r}
integrate(FF, lower = 0, upper = 1, rel.tol = .Machine$double.eps ** .5)
```

function to make graphs automatically:

```{r}
graphpdf <- function(FF, beta, n = 10000, ...) {
  curve(FF, from = 0, to = 1, n = 10000, 
        ylab = "Probability density function",
        main = expression("Plot of function that defines a measure invariant with respect to " ~ T[beta]),
        ...)
  vectposition <- NULL
  #vectexpression <- NULL
  #k <- 1
  #while(k / beta < 1) {
  #  vectposition <- c(vectposition, k / beta)
  #  vectexpression <- c(vectexpression, 
  #                      eval(substitute(expr = expression(r / beta), 
  #                                      env = list(r = k))))
  #  k <- k + 1
  #}
  #for (v in c(1:k/beta,1)) {
  #  abline(v = v, 
  #       lty = 2, 
  #       col = "navy", 
  #       lwd = 3, 
  #       ...)
  #}
  # I tried to add "discontinuity points but I didn't work :(
}
graphpdf(FF = FF, beta = (1 + sqrt(5)) / 2)
```

Example for $\pi$ expansion

```{r}
FF <- Normalise(Sigma1b(beta = pi))
graphpdf(FF = FF, beta = pi)
```

```{r}
integrate(FF, lower = 0, upper = 1, 
          rel.tol = .Machine$double.eps ** .5, 
          subdivisions = 100000)
```

For $e$

```{r}
FF <- Normalise(Sigma1b(beta = exp(1)))
graphpdf(FF = FF, beta = exp(1))
```

```{r}
integrate(FF, lower = 0, upper = 1, 
          rel.tol = .Machine$double.eps ** .5, 
          subdivisions = 100000)
```

For super golden ratio $\psi=\frac{1+\sqrt[3]{\frac{29 + 3\sqrt{93}}{2}} + \sqrt[3]{\frac{29 - 3\sqrt{93}}{2}}}{3}$

```{r}
FF <- Normalise(Sigma1b(beta = 
      (1 + ((29 + 3 * sqrt(93)) / 2) ** (1 / 3) + 
      ((29 - 3 * sqrt(93)) / 2) ** (1 / 3)) / 3))
graphpdf(FF = FF, beta = 
      (1 + ((29 + 3 * sqrt(93)) / 2) ** (1 / 3) + 
      ((29 - 3 * sqrt(93)) / 2) ** (1 / 3)) / 3)
```

```{r}
integrate(FF, lower = 0, upper = 1, 
          rel.tol = .Machine$double.eps ** .5, 
          subdivisions = 100000)
```

For $\frac{1}{\gamma}\approx 1.732455$

```{r}
FF <- Normalise(Sigma1b(beta = 1 / -digamma(1)))
graphpdf(FF = FF, beta = 1 / -digamma(1))
```

```{r}
integrate(FF, lower = 0, upper = 1, 
          rel.tol = .Machine$double.eps ** .5, 
          subdivisions = 100000)
```